Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-16 trunk/constantRate/ConstCompFuzzExt-reorg.tex
wrote our approach in the intro

\paragraph{Our Contributions: Handling Sources with More Errors than Entropy}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\ell$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.

@@

\paragraph{Our Approach}
\bnote{rewrite this!}
Our constructions are computationally secure.  Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).

Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.  Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).

Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}. Our first construction is a \emph{computational fuzzy conductors}.
This may be converted to a computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).

Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.
We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.

Both of our constructions use techniques from Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.  Let $w=w_1 \dots w_\ell$, for $w_j\in \mathcal{Z}$. In the first construction (\consref{cons:first construction}), for each $j$, $\gen$ flips a coin $c_j$ and either obfuscates $I_{w_j}$ or picks a random point $r_j$ and obfuscates $I_{r_j}$.  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rep$ then runs the obfuscated program $P_j$ on $w_j'$ and checks whether $P_j(w_j')=1$.  For most locations $j$, \rep can determine whether $w_j$ or a random value was obfuscated.  Thus, most bits of $c_j$ are recoverable. To tolerate errors,  the set of coins $c_1\dots c_\ell$  is chosen at random from the codewords of an error correcting code. This construction conducts entropy from $w$ to $c$.

Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates). We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then obfuscates each string of blocks. $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block. This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance. We limit the degradation of error-tolerance by using digital lockers in place of point obfuscation~(sufficiently composable point obfuscation implies digital lockers).  This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.  Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed in the first construction. Computational, rather than information-theoretic, analysis seems crucial for achieving this property.

\paragraph{Connection to General Obfuscation}
\bnote{needs to be rewritten}
We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions. Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{brakerski2014virtual,barak2014protecting} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.

>>>>

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\ell$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.

@@

\paragraph{Our Approach}
%\bnote{rewrite this!}
%Our constructions are computationally secure.  Known techniques for proving security of information-theoretic  fuzzy extractors work for all distributions for a given $m, t$, and thus cannot be used with $\Huse\le 0$ (because they would prove security for distributions contained within a single ball of radius of $t$).

%Fuller, Meng, and Reyzin show that replacing secure sketches with a similar computational component is unlikely to be fruitful~\cite[Corollary 3.8, Theorem 3.10]{fuller2013computational}.  Instead, they suggest two alternatives: produce a new consistent secret with computational entropy instead of recovering $w$~(our first construction) or combine the information-reconciliation and privacy amplification components~(our second construction).

Most known constructions of fuzzy extractors put sufficient information in $p$ to recover the original $w$ from a nearby $w'$ during $\rep$ (this procedure is called a \emph{secure sketch}), and then apply a randomness extractor to $w$ to get $r$.
As shown by~\cite{DBLP:journals/siamcomp/DodisORS08}\lnote{specific theorem number} for the information-theoretic case and by \cite[Corollary 3.8, Theorem 3.10]{fuller2013computational} for the computational case, this is unlikely to work for sources with more errors than entropy. Thus, we give up on recovering $w$.

Our first construction reduces the alphabet size by hashing each input symbol (which comes from a large alphabet) into a much smaller set, so that the resulting hash value has low entropy deficiency.
The intuition behind this approach is that it reduces the size of $B_t$ by reducing the alphabet size, but preserves a sufficient portion of the input entropy.  The resulting string no longer has more errors than entropy.
 We then apply any information-theoretic fuzzy extractor to the resulting string

Our second construction, which is only computationally secure, is based on digital lockers~\cite{canetti2008obfuscating}. Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret. The main idea of the construction is to pick a random $r$ and then lock it up in a digital locker that is unlocked by a random subset of the symbols of $w$. To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$. Reusability follows from composability of obfuscation.

Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$. Of course, hiding an entire $r$ in every locker then becomes too risky, since we do not assume that every symbol has high individual entropy. Instead, we hide a single bit per locker (this simplified version of a digital locker is basically point obfuscation). To tolerate errors, these bits come from an error correcting code. And to make sure that the adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor~(\lemref{lem:cond and cext})) from the decoded string.

We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
We need a strong version of point obfuscation/digital lockers that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.

%Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}. Our first construction is a \emph{computational fuzzy conductors}.
%This may be converted to a computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).

%Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.
%We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.

%Both of our constructions use techniques from Canetti and Dakdouk's construction of digital lockers from point obfuscation~\cite{canetti2008obfuscating}.  Let $w=w_1 \dots w_\ell$, for $w_j\in \mathcal{Z}$. In the first construction (\consref{cons:first construction}), for each $j$, $\gen$ flips a coin $c_j$ and either obfuscates $I_{w_j}$ or picks a random point $r_j$ and obfuscates $I_{r_j}$.  This produces $\ell$ obfuscated programs $P_1,..., P_\ell$.  With a close value $w'$, $\rep$ then runs the obfuscated program $P_j$ on $w_j'$ and checks whether $P_j(w_j')=1$.  For most locations $j$, \rep can determine whether $w_j$ or a random value was obfuscated.  Thus, most bits of $c_j$ are recoverable. To tolerate errors,  the set of coins $c_1\dots c_\ell$  is chosen at random from the codewords of an error correcting code. This construction conducts entropy from $w$ to $c$.

%Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates). We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then obfuscates each string of blocks. $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block. This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance. We limit the degradation of error-tolerance by using digital lockers in place of point obfuscation~(sufficiently composable point obfuscation implies digital lockers).  This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.  Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed in the first construction. Computational, rather than information-theoretic, analysis seems crucial for achieving this property.

\paragraph{Connection to General Obfuscation}
\bnote{everything below needs to be rewritten}
We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions. Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{brakerski2014virtual,barak2014protecting} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.
